---
title: "The Carpentries community"
subtitle : "Teaching researchers foundational computational and data science skills"
output: ioslides_presentation
---
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
 
## The Carpentries
 
The Carpentries project comprises diverse global community of volunteer Instructors, Trainers, Maintainers, helpers, and supporters who share a mission to teach foundational computational and data science skills to researchers
 
The main goal of  the carpenteries is not to teach specific skills, per se - although those are covered - but rather, to convey best practices that will enable researchers to be more productive and do better research.
 
 
## What is a Carpentries Workshop?
 
The Carpentries workshops generally comprise two full days of face-to-face instruction, based on either Software Carpentry or Data Carpentry lesson materials, respectively.
 
- Workshops are taught by volunteer certified  instructors who have completed The Carpentries instructor training course.
- Software Carpentry and Data Carpentry lessons are all open source, and are hosted on GitHub. 
 
 
## Software Carpentry vs Data Carpentry
 
Both DC and SWC focus:
 
- on computational skills.
- run two-day workshops taught by volunteer instructors.
- strive to fill gaps in current training for researchers.
 
However, they differ in their content and intended audience.
 
 
## Software Carpentry workshops are:
 
- intended for people who need to program more effectively to solve their computational challenges,
- not domain-specific, and
- modular—each Software Carpentry lesson is standalone.
 
 
 
## Data Carpentry workshops:
 
- are aimed at pure novices,
- are domain-specific, and
- present a full curriculum centered around a single data set.
- focus on best practices surrounding data.
 
 
 
## Data Carpentry lessons:
 
http://www.datacarpentry.org/lessons/
 
 
 
## Slide with Bullets
 
- Bullet 1
- Bullet 2
- Bullet 3
 
## Slide with R Output
 
```{r cars, echo = TRUE}
summary(cars)
```
 
## Slide with Plot
 
```{r pressure}
plot(pressure)
```